\Huge \textcolor{titleTextColor}{ \textsf{\textbf{ \fontsize{85}{60}\selectfont GRASS GIS: a peer-reviewed scientific platform and future research repository }} }

### 2015-03-31 grassposter/2015_EGU_G7_PeerReview_SciPlatform/poster.tex
2015_EGU_G7_PeerReview_SciPlatform poster: better layout for fire fig + caption
git-svn-id: https://svn.osgeo.org/grass/grass-promo@64964 15284696-431f-4ddb-bdfa-cd5b030d7da7

\begin{minipage}{0.5\linewidth}
\includegraphics{fire}
Wildfire simulation in Tangible Landscape environment
\end{minipage}

\begin{minipage}{0.5\linewidth}
%\includegraphics[width=\textwidth]{fire}
% TODO: Something from Europe
\end{minipage}
}

>>>>

\vspace*{-1cm}

\begin{minipage}{0.5\linewidth}
\includegraphics[width=\textwidth]{fire}
Wildfire simulation in Tangible Landscape environment
\end{minipage}
~
\begin{minipage}{0.5\linewidth}
\includegraphics[width=\textwidth]{fire_valencia_040914}
Major wildfire event near Valencia (Spain) between June 28th and July 4th 2012.
The actual perimeters recorded by JRC-EFFIS shown, in 
comparison with burnt area simulated in GRASS GIS.
\end{minipage}
}
